The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-09-25 paper.tex
Added Section on "Repeater Networks" and added sentence on QKD not requiring interferometry

Another approach to linear optics is to pack more features known as degrees of 
freedom onto a single photon, and to increase the degree of control over them. 
It is possible to manipulate degrees of freedom like polarization, time-of-
arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, 
bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals 
for linear optical quantum computations (LOQC) have surfaced 
\cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. 
\sihui {Some of them support new functionalities like secure delegated quantum 
computations \cite{bib:Barz12,bib:Fisher14}}. Others do not promise 
universality in their processing, but still performs tasks such as sampling 
\cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, 
and secure quantum computations \cite{bib:Tan16} that might be hard or 
impossible with a classical system.  Such methods open up new ways to engineer 
quantum states and quantum operations, and expand the toolbox of baseline 
resources we have for implementing quantum computations, which could prove 
crucial in the race to achieve quantum supremacy.

@@

>>>>

Another approach to linear optics is to pack more features known as 
degrees of freedom onto a single photon, and to increase the degree 
of control over them. It is possible to manipulate degrees of
freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, 
bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals 
for linear optical quantum computations (LOQC) have surfaced 
\cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. 
\sihui {Some of them support new functionalities like secure delegated quantum 
computations \cite{bib:Barz12,bib:Fisher14}}. Others do not promise 
universality in their processing, but still performs tasks such as sampling 
\cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, 
and secure quantum computations \cite{bib:Tan16} that might be hard or 
impossible with a classical system.  Such methods open up new ways to engineer 
quantum states and quantum operations, and expand the toolbox of baseline 
resources we have for implementing quantum computations, which could prove 
crucial in the race to achieve quantum supremacy. \sihui{Quantum key distribution (QKD) fundamentally does not require interferometry, but sound QKD protocols using Mach-Zehnder interferometer have been proposed \cite{bib:Sasaki14}, and in some cases realized \cite{bib:Takesue15}.}

@@

\sihui{
\subsection{Repeater networks}
}
